Left-linear rewriting in adhesive categories

### 2024-04-23 concur/fusione.tex
typo

A first class consists of those rewriting systems over
possibly hierarchical graphical structures obtained as algebras of
suitable signatures where rules are constrained not to merge elements
of top level sorts in the hierarchy (e.g., for graphs, nodes can be
merged while edges cannot). The idea here is to consider as graphs presheaves on categories in which there are object which plays the roles of \emph{roots}, i.e.~objects which are not codomains of any arrows beside the identity. \todo{D: quest'ultima frase ha senso?}%We first introduce signatures that are
%essentially acyclic graphs whose nodes can be seen as sorts.

>>>>

A first class consists of those rewriting systems over
possibly hierarchical graphical structures obtained as algebras of
suitable signatures where rules are constrained not to merge elements
of top level sorts in the hierarchy (e.g., for graphs, nodes can be
merged while edges cannot). The idea here is to consider as graphs presheaves on categories in which there are object which plays the roles of \emph{roots}, i.e.~objects which are not codomains of any arrows besides the identity. \todo{D: quest'ultima frase ha senso?}%We first introduce signatures that are
%essentially acyclic graphs whose nodes can be seen as sorts.
